---
title: "IPL batsmen and bowler template"
author: "Tinniam V Ganesh"
date: "March 4, 2017"
output: html_document
---

###1 IPL Batsman setup functions
Get the batsman's details for a batsman

```{r}
setwd("../BattingBowlingDetails")
# IPL Team names
IPLTeamNames <- list("Chennai Super Kings","Deccan Chargers", "Delhi Daredevils","Kings Xi Punjab", 
                  "Kochi Tuskers Kerala","Kolkata Knight Riders","Mumbai Indians","Pune Warriors",
                  "Rajasthan Royals","Royal Challengers Bangalore","Sunrisers Hyderabad","Gujarat Lions",
                  "Rising Pune Supergiants")           


# Check and get the team indices of IPL teams in which the batsman has played
getTeamIndex <- function(batsman){
    setwd("./BattingBowlingDetails")
    load("csk.RData")
    load("dc.RData")
    load("dd.RData")
    load("kxip.RData")
    load("ktk.RData")
    load("kkr.RData")
    load("mi.RData")
    load("pw.RData")
    load("rr.RData")
    load("rcb.RData")
    load("sh.RData")
    load("gl.RData")
    load("rps.RData")
    setwd("..")
    getwd()
    print(ls())
    teams_batsmen = list(csk_batsmen,dc_batsmen,dd_batsmen,kxip_batsmen,ktk_batsmen,kkr_batsmen,mi_batsmen,
                         pw_batsmen,rr_batsmen,rcb_batsmen,sh_batsmen,gl_batsmen,rps_batsmen)
    b <- NULL
    for (i in 1:length(teams_batsmen)){
        a <- which(teams_batsmen[[i]] == batsman)
        
        if(length(a) != 0)
            b <- c(b,i)
    }
    b
}

# Get the list of the IPL team names from the indices passed
getTeams <- function(x){
   
    l <- NULL
    # Get the teams passed in as indexes
    for (i in seq_along(x)){
        
        l <- c(l, IPLTeamNames[[x[i]]]) 
        
    }
    l
}

# Create a consolidated data frame with all teams the IPL batsman has played for
getIPLBatsmanDF <- function(teamNames){
    batsmanDF <- NULL
   # Create a consolidated Data frame of batsman for all IPL teams played
    for (i in seq_along(teamNames)){
       df <- getBatsmanDetails(team=teamNames[i],name=IPLBatsman,dir="./BattingBowlingDetails")
       batsmanDF <- rbind(batsmanDF,df) 
       
    }
    batsmanDF
}

```

###2. Create a consolidated IPL batsman data frame
```{r}
# Since an IPL batsman coculd have played in multiple teams we need to determine these teams and
# create a consolidated data frame for the analysis
# For example to check MS Dhoni we need to do the following

IPLBatsman = "MS Dhoni"
#Check and get the team indices of IPL teams in which the batsman has played
i <- getTeamIndex(IPLBatsman)
    
# Get the team names in which the IPL batsman has played
teamNames <- getTeams(i)
    # Check if file exists in the directory. This check is necessary when moving between matchType


############## Create a consolidated IPL batsman dataframe for analysis
batsmanDF <- getIPLBatsmanDF(teamNames)

```

###3. Runs vs deliveries
```{r}
# For e.g. batsmanName="MS Dhoni""
#batsmanRunsVsDeliveries(batsmanDF, "MS Dhoni")
batsmanRunsVsDeliveries(batsmanDF,"batsmanName")
```

###4. Batsman 4s & 6s
```{r}
batsman46 <- select(batsmanDF,batsman,ballsPlayed,fours,sixes,runs)
p1 <- batsmanFoursSixes(batsman46,"batsmanName")
```

###5. Batsman dismissals
```{r}
batsmanDismissals(batsmanDF,"batsmanName")
```

###6. Runs vs Strike rate
```{r}
batsmanRunsVsStrikeRate(batsmanDF,"batsmanName")
```

###7. Batsman Moving Average
```{r}
batsmanMovingAverage(batsmanDF,"batsmanName")
```


###8. Batsman cumulative average
```{r}
batsmanCumulativeAverageRuns(batsmanDF,"batsmanName")
```

###9. Batsman cumulative strike rate
```{r}
batsmanCumulativeStrikeRate(batsmanDF,"batsmanName")
```

###10. Batsman runs against oppositions
```{r}
batsmanRunsAgainstOpposition(batsmanDF,"batsmanName")
```

###11. Batsman runs vs venue
```{r}
batsmanRunsVenue(batsmanDF,"batsmanName")
```

###12. Batsman runs predict
```{r}
batsmanRunsPredict(batsmanDF,"batsmanName")
```

#######################################################################
# Bowler set up functions
#12
```{r}
setwd("../BattingBowlingDetails")
# IPL Team names
IPLTeamNames <- list("Chennai Super Kings","Deccan Chargers", "Delhi Daredevils","Kings Xi Punjab", 
                  "Kochi Tuskers Kerala","Kolkata Knight Riders","Mumbai Indians","Pune Warriors",
                  "Rajasthan Royals","Royal Challengers Bangalore","Sunrisers Hyderabad","Gujarat Lions",
                  "Rising Pune Supergiants")    



# Get the team indices of IPL teams for which the bowler as played
getTeamIndex_bowler <- function(bowler){
    # Load IPL Bowlers
    setwd("./data")
    load("csk1.RData")
    load("dc1.RData")
    load("dd1.RData")
    load("kxip1.RData")
    load("ktk1.RData")
    load("kkr1.RData")
    load("mi1.RData")
    load("pw1.RData")
    load("rr1.RData")
    load("rcb1.RData")
    load("sh1.RData")
    load("gl1.RData")
    load("rps1.RData")
    setwd("..")
    teams_bowlers = list(csk_bowlers,dc_bowlers,dd_bowlers,kxip_bowlers,ktk_bowlers,kkr_bowlers,mi_bowlers,
                         pw_bowlers,rr_bowlers,rcb_bowlers,sh_bowlers,gl_bowlers,rps_bowlers)
    b <- NULL
    for (i in 1:length(teams_bowlers)){
        a <- which(teams_bowlers[[i]] == bowler)
        if(length(a) != 0){
            b <- c(b,i)
        }
    }
    b
}


# Get the list of the IPL team names from the indices passed
getTeams <- function(x){
   
    l <- NULL
    # Get the teams passed in as indexes
    for (i in seq_along(x)){
        
        l <- c(l, IPLTeamNames[[x[i]]]) 
        
    }
    l
}

# Get the team names
teamNames <- getTeams(i)

getIPLBowlerDF <- function(teamNames){
    bowlerDF <- NULL
    
    # Create a consolidated Data frame of batsman for all IPL teams played
    for (i in seq_along(teamNames)){
          df <- getBowlerWicketDetails(team=teamNames[i],name=IPLBowler,dir="./BattingBowlingDetails")
          bowlerDF <- rbind(bowlerDF,df) 
        
    }
    bowlerDF
}
```

### 13. Get the consolidated data frame for an IPL bowler
```{r}
# Since an IPL bowler could have played in multiple teams we need to determine these teams and
# create a consolidated data frame for the analysis
# For example to check R Ashwin we need to do the following

IPLBowler = "R Ashwin"
#Check and get the team indices of IPL teams in which the batsman has played
i <- getTeamIndex(IPLBowler)
    
# Get the team names in which the IPL batsman has played
teamNames <- getTeams(i)
    # Check if file exists in the directory. This check is necessary when moving between matchType


############## Create a consolidated IPL batsman dataframe for analysis
bowlerDF <- getIPLBowlerDF(teamNames)

```


###14. Bowler Mean Economy rate
```{r}
# For e.g. to get the details of R Ashwin do
#bowlerMeanEconomyRate(bowlerDF,"R Ashwin")
bowlerMeanEconomyRate(bowlerDF,"bowlerName")
```

###15. Bowler mean runs conceded
```{r}
bowlerMeanRunsConceded(bowlerDF,"bowlerName")
```

###16. Bowler Moving Average
```{r}
bowlerMovingAverage(bowlerDF,"bowlerName")
```

###17. Bowler cumulative average wickets
```{r}
bowlerCumulativeAvgWickets(bowlerDF,"bowlerName")
```

###18. Bowler cumulative Economy Rate (ER)
```{r}
bowlerCumulativeAvgEconRate(bowlerDF,"bowlerName")
```

###19. Bowler wicket plot
```{r}
bowlerWicketPlot(bowlerDF,"bowlerName")
```

###20. Bowler wicket against opposition
```{r}
bowlerWicketsAgainstOpposition(bowlerDF,"bowlerName")
```


###21. Bowler wicket at cricket grounds
```{r}
bowlerWicketsVenue(bowlerDF,"bowlerName")
```

###22. Predict number of deliveries to wickets
```{r}
setwd("./IPLMatches")
bowlerDF1 <- getDeliveryWickets(team="IPLTeam1",dir=".",name="bowlerName",save=FALSE)
bowlerWktsPredict(bowlerDF1,"bowlerName")
```
