---
title: "IPL Matches between 2 Teams"
author: "Tinniam V Ganesh"
date: "March 4, 2017"
output: html_document
---

###1 IPL Matches between 2 teams 
Load  match data between any 2 teams from ./IPLMatchesBetween2Teams for e.g.Delhi Daredevils-Royal Challengers Bangalore-allMatches

```{r}
setwd("./IPLMatchesBetween2Teams")
load("Delhi Daredevils-Royal Challengers Bangalore-allMatches.RData")
dd_rcb_matches <- matches
#Replace below with your own countries
IPLTeam1<-"Delhi Daredevils"
IPLTeam2 <- "Royal Challengers Bangalore"
IPLTeam1VsIPLTeam2 <- paste(IPLTeam1,"-",IPLTeam2,"-allMatches.RData",sep="")
load(IPLTeam1VsIPLTeam2)
IPLTeam1_IPLTeam2_matches <- matches

```

###2.Batsmen partnerships
```{r}
m<- teamBatsmenPartnershiOppnAllMatches(IPLTeam1_IPLTeam2_matches,"IPLTeam1",report="summary")
m
m<- teamBatsmenPartnershiOppnAllMatches(IPLTeam1_IPLTeam2_matches,"IPLTeam2",report="summary")
m
m<- teamBatsmenPartnershiOppnAllMatches(IPLTeam1_IPLTeam2_matches,"IPLTeam1",report="detailed")
m
teamBatsmenPartnershipOppnAllMatchesChart(IPLTeam1_IPLTeam2_matches,"IPLTeam1","IPLTeam2")
```

###3. Team batsmen vs bowlers
```{r}
teamBatsmenVsBowlersOppnAllMatches(IPLTeam1_IPLTeam2_matches,"IPLTeam1","IPLTeam2")
```

###4. Bowling scorecard
```{r}
a <-teamBattingScorecardOppnAllMatches(IPLTeam1_IPLTeam2_matches,main="IPLTeam1",opposition="IPLTeam2")
a
```

###5. Team bowling performance
```{r}
teamBowlingPerfOppnAllMatches(IPLTeam1_IPLTeam2_matches,main="IPLTeam1",opposition="IPLTeam2")
```

###6. Team bowler wickets
```{r}
teamBowlersWicketsOppnAllMatches(IPLTeam1_IPLTeam2_matches,main="IPLTeam1",opposition="IPLTeam2")
m <-teamBowlersWicketsOppnAllMatches(IPLTeam1_IPLTeam2_matches,main="IPLTeam1",opposition="IPLTeam2",plot=FALSE)
teamBowlersWicketsOppnAllMatches(IPLTeam1_IPLTeam2_matches,"IPLTeam1","IPLTeam2",top=3)
m
```

###7. Team bowler vs batsmen
```{r}
teamBowlersVsBatsmenOppnAllMatches(IPLTeam1_IPLTeam2_matches,"IPLTeam1","IPLTeam2",top=5)
```

###8. Team bowler wicket kind
```{r}
teamBowlersWicketKindOppnAllMatches(IPLTeam1_IPLTeam2_matches,"IPLTeam1","IPLTeam2",plot=TRUE)
m <- teamBowlersWicketKindOppnAllMatches(IPLTeam1_IPLTeam2_matches,"IPLTeam1","IPLTeam2",plot=FALSE)
m[1:30,]
```

###9. Team bowler wicket runs
```{r}
teamBowlersWicketRunsOppnAllMatches(IPLTeam1_IPLTeam2_matches,"IPLTeam1","IPLTeam2")
```

###10. Plot wins and losses
```{r}
setwd("./IPLMatches")
plotWinLossBetweenTeams("IPLTeam1","IPLTeam2")
```

