---
title: "IPL Templates with yorkr"
author: "Tinniam V Ganesh"
date: "March 4, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this post I create yorkr templates for end-to-end analysis of IPL T20 matches that are available 
on [Cricsheet](http://cricsheet.org/ ). With these templates you can convert all
IPL data which is in yaml format to R dataframes. Further I create data and the necessary 
templates for analyzing IPL matches, teams and players. All of these can be accessed at [yorkrIPLTemplate](https://github.com/tvganesh/yorkrIPLTemplate). The templates are


1. Template for conversion and setup - IPLT20Template.Rmd
1. Any IPL match - IPLMatchtemplate.Rmd
2. IPL matches between 2 nations - IPLMatches2TeamTemplate.Rmd
3. A IPL nations performance against all other IPL nations - IPLAllMatchesAllOppnTemplate.Rmd
4. Analysis of IPL batsmen and bowlers of all IPL nations - IPLBatsmanBowlerTemplate.Rmd

Besides the templates the repository also includes the converted data for all IPL 
matches I downloaded  from Cricsheet in Dec 2016. So this data is complete till the 2016 IPL season.
You can recreate the files as more matches are added to Cricsheet site in IPL 2017 and future seasons. 
This post contains all the steps needed for detailed analysis of IPL matches, teams and IPL player. This will also be my reference in future if I decide to analyze IPL in future!

There will be 5 folders at the root

1. IPLdata - Match files as yaml from Cricsheet
2. IPLMatches - Yaml match files converted to dataframes
3. IPLMatchesBetween2Teams - All Matches between any 2 IPL teams
4. allMatchesAllOpposition - An IPL teams's performance against all other teams
5. BattingBowlingDetails - Batting and bowling details of all IPL teams

```{r}
library(yorkr)
library(dplyr)
```
The first few steps take care of the  data setup. This needs
to be done before any of the analysis of IPL batsmen, bowlers, any IPL match,
matches between any 2 IPL countries or analysis of a teams performance against all
other countries

There will be 5 folders at the root

1. data
2. IPLMatches
3. IPLMatchesBetween2Teams
4. allMatchesAllOpposition
5. BattingBowlingDetails


# The source YAML files will be in IPLData folder
# 1.Create directory of IPLMatches
Some files may give  conversions errors. You could try to debug the
problem or just remove it from the IPLdata folder. At most  2-4 file will have 
conversion problems and I usally remove then from the files to be 
converted. 

Also take a look at my [GooglyPlus](https://tvganesh.shinyapps.io/googlyPlus/) shiny
app which was created after performing the same conversion on the Dec 16 data
.

```{r }
convertAllYaml2RDataframesT20("data","IPLMatches")
```

### 2.Save all matches between all combinations of IPL nations
This function will create the set of all matches between each IPL team
against every other IPL team. This uses the data that was created in IPLMatches,
with the convertAllYaml2RDataframesIPL() function.
```{r}
setwd("./IPLMatchesBetween2Teams")
saveAllMatchesBetween2IPLTeams("../IPLMatches")
```

### 3.Save all matches against all opposition
This will create a consolidated dataframe of all matches played by every IPL playing
nation against all other nattions. This also uses the data that was created in IPLMatches,
with the convertAllYaml2RDataframesIPL() function.
```{r}
setwd("../allMatchesAllOpposition")
saveAllMatchesAllOppositionIPLT20("../IPLMatches")
```

###4. Create batting and bowling details for each IPL team
These are the current IPL playing teams. You can add to this vector
as newer IPL teams start playing IPL. You will get to know all IPL teams
by also look at the directory created above namely allMatchesAllOpposition.
This also uses the data that was created in IPLMatches,
with the convertAllYaml2RDataframesIPL() function.
```{r}
setwd("../BattingBowlingDetails")
ipl_teams <- list("Chennai Super Kings","Deccan Chargers", "Delhi Daredevils","Kings XI Punjab", 
              "Kochi Tuskers Kerala","Kolkata Knight Riders","Mumbai Indians","Pune Warriors",
              "Rajasthan Royals","Royal Challengers Bangalore","Sunrisers Hyderabad","Gujarat Lions",
                 "Rising Pune Supergiants")

for(i in seq_along(ipl_teams)){
    print(ipl_teams[i])
    val <- paste(ipl_teams[i],"-details",sep="")
    val <- getTeamBattingDetails(ipl_teams[i],dir="../IPLMatches", save=TRUE)

}

for(i in seq_along(ipl_teams)){
    print(ipl_teams[i])
    val <- paste(ipl_teams[i],"-details",sep="")
    val <- getTeamBowlingDetails(ipl_teams[i],dir="../IPLMatches", save=TRUE)

}
```

###5. Get the list of batsmen for a particular IPL team
The following code is needed for analyzing individual IPL batsmen. In IPL a player could have played in
multiple IPL teams.

```{r}
getBatsmen <- function(df){
    bmen <- df %>% distinct(batsman) 
    bmen <- as.character(bmen$batsman)
    batsmen <- sort(bmen)
}
load("Chennai Super Kings-BattingDetails.RData")
csk_details <- battingDetails
load("Deccan Chargers-BattingDetails.RData")
dc_details <- battingDetails
load("Delhi Daredevils-BattingDetails.RData")
dd_details <- battingDetails
load("Kings XI Punjab-BattingDetails.RData")
kxip_details <- battingDetails
load("Kochi Tuskers Kerala-BattingDetails.RData")
ktk_details <- battingDetails
load("Kolkata Knight Riders-BattingDetails.RData")
kkr_details <- battingDetails
load("Mumbai Indians-BattingDetails.RData")
mi_details <- battingDetails
load("Pune Warriors-BattingDetails.RData")
pw_details <- battingDetails
load("Rajasthan Royals-BattingDetails.RData")
rr_details <- battingDetails
load("Royal Challengers Bangalore-BattingDetails.RData")
rcb_details <- battingDetails
load("Sunrisers Hyderabad-BattingDetails.RData")
sh_details <- battingDetails
load("Gujarat Lions-BattingDetails.RData")
gl_details <- battingDetails
load("Rising Pune Supergiants-BattingDetails.RData")
rps_details <- battingDetails

#Get the batsmen for each IPL team
csk_batsmen <- getBatsmen(csk_details)
dc_batsmen <- getBatsmen(dc_details)
dd_batsmen <- getBatsmen(dd_details)
kxip_batsmen <- getBatsmen(kxip_details)
ktk_batsmen <- getBatsmen(ktk_details)
kkr_batsmen <- getBatsmen(kkr_details)
mi_batsmen <- getBatsmen(mi_details)
pw_batsmen <- getBatsmen(pw_details)
rr_batsmen <- getBatsmen(rr_details)
rcb_batsmen <- getBatsmen(rcb_details)
sh_batsmen <- getBatsmen(sh_details)
gl_batsmen <- getBatsmen(gl_details)
rps_batsmen <- getBatsmen(rps_details)

# Save the dataframes
save(csk_batsmen,file="csk.RData")
save(dc_batsmen, file="dc.RData")
save(dd_batsmen, file="dd.RData")
save(kxip_batsmen, file="kxip.RData")
save(ktk_batsmen, file="ktk.RData")
save(kkr_batsmen, file="kkr.RData")
save(mi_batsmen , file="mi.RData")
save(pw_batsmen, file="pw.RData")
save(rr_batsmen, file="rr.RData")
save(rcb_batsmen, file="rcb.RData")
save(sh_batsmen, file="sh.RData")
save(gl_batsmen, file="gl.RData")
save(rps_batsmen, file="rps.RData")
```

###6. Get the list of bowlers for a particular IPL team
The method below can get the list of bowler names for any IPL team.The following code is needed for analyzing individual IPL bowlers. In IPL a player could have played in multiple IPL teams.

```{r}
getBowlers <- function(df){
    bwlr <- df %>% distinct(bowler) 
    bwlr <- as.character(bwlr$bowler)
    bowler <- sort(bwlr)
}

load("Chennai Super Kings-BowlingDetails.RData")
csk_details <- bowlingDetails
load("Deccan Chargers-BowlingDetails.RData")
dc_details <- bowlingDetails
load("Delhi Daredevils-BowlingDetails.RData")
dd_details <- bowlingDetails
load("Kings XI Punjab-BowlingDetails.RData")
kxip_details <- bowlingDetails
load("Kochi Tuskers Kerala-BowlingDetails.RData")
ktk_details <- bowlingDetails
load("Kolkata Knight Riders-BowlingDetails.RData")
kkr_details <- bowlingDetails
load("Mumbai Indians-BowlingDetails.RData")
mi_details <- bowlingDetails
load("Pune Warriors-BowlingDetails.RData")
pw_details <- bowlingDetails
load("Rajasthan Royals-BowlingDetails.RData")
rr_details <- bowlingDetails
load("Royal Challengers Bangalore-BowlingDetails.RData")
rcb_details <- bowlingDetails
load("Sunrisers Hyderabad-BowlingDetails.RData")
sh_details <- bowlingDetails
load("Gujarat Lions-BowlingDetails.RData")
gl_details <- bowlingDetails
load("Rising Pune Supergiants-BowlingDetails.RData")
rps_details <- bowlingDetails

# Get the bowlers for each team
csk_bowlers <- getBowlers(csk_details)
dc_bowlers <- getBowlers(dc_details)
dd_bowlers <- getBowlers(dd_details)
kxip_bowlers <- getBowlers(kxip_details)
ktk_bowlers <- getBowlers(ktk_details)
kkr_bowlers <- getBowlers(kkr_details)
mi_bowlers <- getBowlers(mi_details)
pw_bowlers <- getBowlers(pw_details)
rr_bowlers <- getBowlers(rr_details)
rcb_bowlers <- getBowlers(rcb_details)
sh_bowlers <- getBowlers(sh_details)
gl_bowlers <- getBowlers(gl_details)
rps_bowlers <- getBowlers(rps_details)

#Save the dataframes
save(csk_bowlers,file="csk1.RData")
save(dc_bowlers, file="dc1.RData")
save(dd_bowlers, file="dd1.RData")
save(kxip_bowlers, file="kxip1.RData")
save(ktk_bowlers, file="ktk1.RData")
save(kkr_bowlers, file="kkr1.RData")
save(mi_bowlers , file="mi1.RData")
save(pw_bowlers, file="pw1.RData")
save(rr_bowlers, file="rr1.RData")
save(rcb_bowlers, file="rcb1.RData")
save(sh_bowlers, file="sh1.RData")
save(gl_bowlers, file="gl1.RData")
save(rps_bowlers, file="rps1.RData")
```

### Now we are all set

